An Automatic Verification Framework for Software Configurations

### 2016-05-08 OSDI/arch.tex
better arch

We propose \app, an automatic verification framework for 
software configuration files.
In particular, \app can solve many sophisticated 
configuration errors (\eg, ordering errors, missing entry errors 
and fine-grained value correlation) that previous efforts cannot 
detect. As depicted in Figure~\ref{fig-overview}, 
a typical \app verification workflow has three steps:
translation, learning and checking. In this section, we briefly
describe how does each step work.

@@

\para{Translator.}
The translator module first parses the input sample 
dataset (containing both configuration files and system environment
information), and then transforms them to a more structured
and typed intermediate representation.
When we run type inference on a configuration file, 
the type of a variable cannot always be fully determined from 
a single value.
We address this problem 
by introducing so called {\em probabilistic types}.
Rather than giving a variable a single type, 
we assign several types with their probability distributions. 
We can later use these more structured files
as a training set to learn the rules.

>>>>

We propose \app, an automatic verification framework for 
software configuration files.
In particular, \app can solve many sophisticated 
configuration errors (\eg, ordering errors, missing entry errors,
and fine-grained value correlation) that previous efforts cannot 
detect. As depicted in Figure~\ref{fig-overview}, 
a typical \app verification workflow has three steps:
translation, learning, and checking. In this section, we briefly
describe how does each step work.

@@

\para{Translator.}
The translator module first parses the input sample 
dataset (containing both configuration files and system environment
information), and then transforms them to a more structured
and typed intermediate representation.
When we run type inference on a configuration file, 
the type of a variable cannot always be fully determined from 
a single value.
We address this problem 
by introducing {\em probabilistic types}.
Rather than giving a variable a single type, 
we assign several types over a probability distribution. 
We can later use these more structured files
as a training set to learn the rules.
